Transition from forest to agriculture in the Brazilian Amazon from 1985 to 2021

### 2022-11-17 manuscript/manuscript.Rmd
Add reference. Add TODO. Lining format was changed.

Brazil policies since the 1960s were focused on the expansion of the frontier in the Amazon, specially focused in economic income and land security [@Carvalho2002; @Mcdonald2003].
Such development model led to the construction of thousands of kilometers of roads, and the settlement of large scale livestock farms [@Carvalho2002].
This period was marked with high rates of deforestation of mature forests [@Fearnside2005].
At the same time, cattle and soybean productions started to move to the north direction in the Brazilian territory, in which soybeans cultivation areas followed cattle ranches expansion over the Amazon forest [@Simon2005].
This pattern of extensive livestock occupation after deforestation, followed by the establishment of annual crops is very characteristics in the Amazon biome, and persists nowadays.
This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

TODO: Talk about the Avança Brasil plan [@Carvalho2002].

>>>>

Brazil policies since the 1960s were focused on the expansion of the frontier in the Amazon, specially focused in economic income and land security [@Carvalho2002; @Mcdonald2003; @Banerjee2009]. Such development model led to the construction of thousands of kilometers of roads, and the settlement of large scale livestock farms [@Carvalho2002; @Banerjee2009]. This period was marked with high rates of deforestation of mature forests [@Fearnside2005]. At the same time, cattle and soybean productions started to move to the north direction in the Brazilian territory, in which soybeans cultivation areas followed cattle ranches expansion over the Amazon forest [@Simon2005]. This pattern of extensive livestock occupation after deforestation, followed by the establishment of annual crops is very characteristics in the Amazon biome, and persists nowadays. This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

TODO: Talk about public policies from 1985 to 2000 (greater carajas program, national environmental policy) [@Banerjee2009].

TODO: Talk about the Avança Brasil plan [@Carvalho2002; @Banerjee2009].

TODO: confront our results with Morton 2006 (see the year of 2003).
